---
title: Standardized Plots for Presentation of MSE Results in IOTC
author: Iago Mosqueira (EC JRC) <iago.mosqueira@ec.europa.eu>
date: "`r format(Sys.time(), '%d %B, %Y')`"
tags:
abstract:
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Standardized Plots for Presentation of MSE Results in IOTC}
  %\usepackage[UTF-8]{inputenc}
---

license: Creative Commons Attribution-ShareAlike 4.0 International Public License
---

```{r, start, echo=FALSE, message=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
  fig.width=5, fig.height=3, fig.pos='H')
```

```{r pkgs}
library(mseviz)
```

# Inputs

```{r data}
data(perf)
data(omruns)
```

## Performance levels across MPs

These are the necessary columns in the performance `data.frame`

- *indicator*, indicator code
- *year*
- *data*, computed value
- *iter*, iteration number
- *name*, indicator name
- *mp*, MP name

```{r perf}
perf
```

## Time series of results of MP runs

- *mp*, MP name
- *year*
- *data*, computed value
- *iter*, iteration number
- *qname*, computed metric, e.g. Catch (C), mean F (F)

```{r runs}
runs
```

## Time series of OM history

- *year*
- *data*, computed value
- *iter*, iteration number
- *qname*, computed metric, e.g. Catch (C), mean F (F)

```{r om}
om
```

# Standard IOTC MSE plots

## plotBPs, indicators boxplots

```{r plotbps}
plotBPs(perf, indicators=c("T1", "S6", "F2", "Y1", "S3"))
```

## plotTOs, trade-off plots

```{r plottos}
plotTOs(perf, x="Y1", y=c("S3", "S6", "F2", "T1"))
```

## kobeMPs, performance on Kobe plot

```{r kobemps}
kobeMPs(perf)
```

## kobe2MPs,

## plotOMruns, time series of OM and MPs

```{r plotomrunsf}
data(omruns)
#plotOMruns(om[qname=="F",], runs[qname=="F",], limit=0.8, target=0.4)
```

```{r plotomrunsc}
plot(9)
#plotOMruns(om[qname=="C",], runs[qname=="C",])
```

# IOTC MSE output tables

## perftable

## fullperftable


# References
